Enhancing the sales prediction of newly published books by means of computational intelligence methods

### 2016-01-14 paper.tex
Quitada la figura 1

\begin{figure}[!ht] 
\begin{center}
  \epsfig{file=stages.eps,width=7cm}
\caption{\small{Three main stages in a typical sales prediction process: data analysis, (2) forecasting 
methods testing, and (3) subjectively adjusting the obtained results.}}
\label{fig:stages}
\end{center}
\end{figure}

@@

In some cases, depending on the company needs and after obtaining the forecasting 
results, it is necessary a third stage where experienced 
managers adjust subjectively the results obtained using the forecasting methods 
(see Figure \ref{fig:stages} for details). 
They might manually adjust the forecasting results taking into account their 
knowledge in industry experience and their perception about trends.

>>>>

\hspace{2cm}
\begin{verbatim}
Stage 1: Collecting and analyze data
		- Variables selection
 		- Data preprocesing
Stage 2: Select the best forecasting method
 		- Obtaining and evaluating forecasting models
 		- Calculate forecasting values
Stage 3: Subjectively adjust obtained results
		- Apply additional expert knowledge, such as information 
 		  about seasonality, trends, etc.
\end{verbatim}

% Maribel: quito la figura por el issue asignado por antonio mora.
%\begin{figure}[!ht] 
%\begin{center}
%  \epsfig{file=stages.eps,width=7cm}
%\caption{\small{Three main stages in a typical sales prediction process: data analysis, (2) forecasting 
%methods testing, and (3) subjectively adjusting the obtained results.}}
%\label{fig:stages}
%\end{center}
%\end{figure}

@@

%In some cases, depending on the company needs and after obtaining the forecasting  results, it is necessary a third stage where experienced managers adjust subject1ively the results obtained using the forecasting methods (see Figure \ref{fig:stages} for details). Esta frase no aporta nada que no esté dicho ya antes en los comentarios de las tres etapas que antes estaban en una figura, así que quito la frase entera: Maribel

They might manually adjust the forecasting results taking into account their 
knowledge in industry experience and their perception about trends.
